Wolfram Lanauge interop with Wolframite - DRAFT

### 2024-01-25 docs/projects/math/wolframite/index.qmd
Wolframite - rerendered

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: index.html}
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

@@

>>>>

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: index.html}
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}
title: Wolfram Lanauge interop with Wolframite - DRAFT
author: Daniel Slutsky

@@

This notebook demonstrates basic usage of [Wolframite](https://github.com/scicloj/wolframite/) in a way that would work in visual tools supporting [Kindly](https://scicloj.github.io/kindly-noted/kindly).
It is mostly copied and adpated from [the official Wolframite demo](https://github.com/scicloj/wolframite/blob/main/dev/demo.clj).
